What do incoming university students believe about open science practices in

### 2021-03-09 analysis/Manuscript.Rmd
start on calculating differences between norms

## Data analysis
<!-- Can we move this to a reproducible code statement at the end? It works now -->

>>>>

## Data analysis

```{r, difference between norm and counternorm}

# select columns that relate to norms & pivot it long
norm_long <- df %>% 
  select(c(id, ends_with("_norm"))) %>% 
    pivot_longer (cols = ends_with("norm"),
                names_to = "practice",
                values_to = "norm rating")

# remove "_norm" from the practice variables
norm_long$practice = gsub(pattern = "_norm", replacement = "", x = norm_long$practice)

# select columns that relate to counternorms
cnorm_long <- df %>% 
  select(c(id, ends_with("_cnorm"))) %>% 
  pivot_longer (cols = ends_with("cnorm"),
                names_to = "practice",
                values_to = "cnorm rating")

# remove "_cnorm" from the practice variables
cnorm_long$practice = gsub(pattern = "_cnorm", replacement = "", x = cnorm_long$practice)

# join the norm and counternorm tibbles
norm_cnorm <- norm_long %>% inner_join(cnorm_long)

# create a `diff` variable that is the counternorm subtracted from the norm
norm_cnorm <- norm_cnorm %>% 
  mutate (diff = (`norm rating` - `cnorm rating`)) %>% 
      dplyr::select(-(`id`)) # remove this now that I've confirmed it works

norm_means <- norm_cnorm %>% 
    dplyr::group_by(practice) %>%  
    summarise(norm_mean = mean(`norm rating`, na.rm = TRUE), 
              norm_sd = sd(`norm rating`, na.rm = TRUE), 
              cnorm_mean = mean(`cnorm rating`, na.rm = TRUE), 
              cnorm_sd = sd(`cnorm rating`, na.rm = TRUE), 
              diff_mean = mean(`diff`, na.rm = TRUE), 
              diff_sd = sd(`diff`, na.rm = TRUE)) %>% 
  ungroup()

# breadcrumb: I need to use papaja tables....
# pull means & sd into the same column with (sd) in parentheses
# headings should then be norm, counternorm, difference

knitr::kable(norm_means,
             caption = "Means (sd) for norms, counternorms, and the difference between the two for each of the practices",
             digits = 2,
             align = c('lcccccc'))

# breadcrumbs: rename the practices so it's easier to read

# I don't need this...
# norm_means <- norm_cnorm %>% 
    # select(-id) %>% 
    # group_by(practice) %>%  
    # mutate(norm_mean = mean(`norm rating`, na.rm = TRUE)) %>% 
    # mutate(norm_sd = sd(`norm rating`, na.rm = TRUE)) %>% 
    # mutate(cnorm_mean = mean(`cnorm rating`, na.rm = TRUE)) %>% 
    # mutate(cnorm_sd = sd(`cnorm rating`, na.rm = TRUE)) %>% 
    # mutate(diff_mean = mean(`diff`, na.rm = TRUE)) %>% 
    # mutate(diff_sd = sd(`diff`, na.rm = TRUE))

```{r, eval=FALSE}
# I'm sure there's a fancier way to subtract the counternorm from the norm, 
  # but for now we will do this...

norms <-  vars_select(names(df), ends_with('_norm'))
cnorms <-  vars_select(names(df), ends_with('_cnorm'))

miss_fun = function(x){
  sum(is.na(x))
}

diff_fun = function(x, y){
  (norms - cnorms)
}

diff_fun(x = norms, y = cnorms)

df$diff <- apply(X = df[, ], MARGIN = 1, FUN = miss_fun)

\newpage
# Reproducible Code Statement
